Pulling oral and IV data from CvTdb

### 2023-01-06 Working Rmds/pulling_oral_iv_data_cvtdb.Rmd
Made a change to dose units for PCB-126 study (was mg/kg; I think it should be ng/kg).

```{r}
fpath <- "C:/Users/cring/OneDrive - Environmental Protection Agency (EPA)/CvTdb/"
this_date <- format(Sys.time(), "%Y_%m_%d_%H_%M_%S")

@@

>>>>

```{r}
fpath <- "C:/Users/cring/OneDrive - Environmental Protection Agency (EPA)/CvTdb/"
this_date <- format(Sys.time(), "%Y_%m_%d")

@@

## Correcting dose level units for PCB-126

Upon examining PCB-126, I think the original dose units should be ng/kg rather than mg/kg. If we look at https://cebs.niehs.nih.gov/cebs/study/002-02863-0008-0000-9 and look at the summary data rather than individual animal data, the dose units are listed as "ng/kg." In the rest of the studies at https://cebs.niehs.nih.gov/cebs/test_article/57465-28-8 all of the dosing units are ng/kg. So I think that is what it should be.

```{r}
cvt_data[chemicals_dosed.dsstox_substance_id %in% "DTXSID3032179", studies.dose_level_original := "ng/kg"]
cvt_data[chemicals_dosed.dsstox_substance_id %in% "DTXSID3032179", studies.dose_level_normalized_corrected := as.numeric(studies.dose_level_normalized) * 1e-6] #convert to mg/kg
```
